Working title: Ecological network control

### 2018-06-17 paper/manuscript.Rmd
Models of control capacity / superior
Close #32

---
title: "Working title: Ecological network control"
classoption: a4paper
csl: journal-of-ecology.csl
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    number_sections: false
toc: false
header-includes:
- \usepackage{geometry}
# - \geometry{right=3in,marginparwidth=2.5in}
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{caption}
- \usepackage{lineno}
- \usepackage{xr}
- \externaldocument[S-]{supp-info}
- \usepackage{multirow}
- \usepackage{tabu}
- \usepackage{makecell}
documentclass: artikel1
bibliography: references.bib
---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE)
options(knitr.kable.NA = '')
```

@@

```{r correlation-calculations}
drake::loadd(sl_char_corr)
correlations <- sl_char_corr %>% 
  extract2("mean") %>%
  as.data.frame() %>%
  tibble::rownames_to_column() %>%
  dplyr::filter(!rowname %in% c("control_capacity", "superior"))
```

The control capacity $\phi$ and the likelihood of being a superior node $\sigma$ are weakly correlated with commonly used centrality metrics. 
Specifically, the correlation coefficient between the control capacity $\phi$ and other metrics ranged between `r round(min(correlations$control_capacity), 2)` and `r round(max(correlations$control_capacity), 2)` while the correlation coefficient between the likelyhood of being a superior node $\sigma$ and the centrality metrics ranged between `r round(min(correlations$superior), 2)` and `r round(max(correlations$superior), 2)` (Figure \@ref(fig:fig-correlogram)).

Both plants and pollinators were distributed across a gradient of control capacity and wether they were superior nodes or not (Figure \@ref(fig:fig-species-level)). 
This distribution, in particular for control capacity, was independent of the degree of species. 
Remarkably, every single invasive plant species in our dataset had both the maximum control capacity and was classified as a superior node.

```{r fig-species-level, fig.width=fig_sizes()[[2]]*2/3, fig.height=fig_sizes()[[1]], fig.cap="Control capacity and "}
drake::loadd(fig_control_capacity)
library(ggplot2)
fig_control_capacity[[2]] <- fig_control_capacity[[2]] +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank())
fig_control_capacity[[4]] <- fig_control_capacity[[4]] +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank())

>>>>

---
title: "Working title: Ecological network control"
classoption: a4paper
csl: journal-of-ecology.csl
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    number_sections: false
toc: false
header-includes:
- \usepackage{geometry}
# - \geometry{right=3in,marginparwidth=2.5in}
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{caption}
- \usepackage{lineno}
- \usepackage{xr}
- \externaldocument[S-]{supp-info}
- \usepackage{siunitx}
- \usepackage{multirow}
- \usepackage{makecell}
- \usepackage{threeparttablex}
documentclass: artikel1
bibliography: references.bib
---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE)
options(knitr.kable.NA = '---')
```

@@

The models that best explained a species control capacity $\phi$, had a random intercept and slope for the species asymmetry grouped by guild (plants or pollinators; Table \@ref(S-tab:tab-model-output-control-capacity)). 
Contribution to nestedness was the most important variable followed by visitation strength (Table \@ref(tab:tab-model-selection-table), \@ref(S-tab:tab-var-importance)). 
Species with large contribution to nestedness and large visitation strength were more likely to have a large control capacity (Figure \@ref(fig:fig-species-level)a and b). 
For the probability of being a superior node $\sigma$, the most parsimonuous models did not include any random effect (Table \@ref(S-tab:tab-model-output-superior)). 
The most important variables were the species asymmetry and the visitation strength (Table \@ref(tab:tab-model-selection-table), \@ref(S-tab:tab-var-importance)). 
Specifically, species with a positive asymmetry (this is they affect their partners more than what their parners affect them), and with a large visitatin strength were more likely to be superior nodes (Figure \@ref(fig:fig-species-level)c and d). 
Furthermore, degree was positively, but only weakly asociated to both control capacity and the probability of being a superior node. 
Remarkably, many species with a low degree, especially pollinators attained a large control capacity in their communities \@ref(S-fig:fig-species-models-degree).

dplyr::bind_rows(cc_table, su_table) %>%
  dplyr::select(-logLik, - AICc) %>%
  knitr::kable("latex", 
               col.names = c("int.", "deg.", "asy.", "nes.", "str.", "d.f.",  "$\\Delta$AICc","weight"),
               booktabs = T, 
               caption = "Selection table of the generalised mixed effect models of control capacity $\\phi$ and the probability of being a superior node $\\sigma$. Only models with a weight larger than 0.01 are shown. All variables were scaled and so the effect sizes are comparable.", 
               row.names = F, 
               digits = 2, 
               escape = F) %>%
  kableExtra::add_header_above(c("effect sizes" = 5, " " = 3), escape = F) %>%
  kableExtra::kable_styling(font_size = 8) %>%
  kableExtra::group_rows("control capacity models", 1, nrow(cc_table)) %>%
  kableExtra::group_rows("superior probability models", nrow(cc_table) + 1, nrow(cc_table) + nrow(su_table)) %>%
  kableExtra::footnote(general = "intercept (int), degree (deg), asymmetry (asy), visitation strength (str).", 
                       general_title = "Terms: ", 
                       footnote_as_chunk = TRUE, 
                       threeparttable = TRUE)
```

```{r fig-species-level, fig.width=fig_sizes()[[2]]*2/3, fig.height=fig_sizes()[[1]], fig.cap="Relationship between the most important variables in the models of control capacity (a, b) and the probability of being a superior node (c, d). The plots show the values predicted by most parsimonious model for each response variable. The model for control capacity include a random effect for the trophic guild , while the model of superior probability does not include any random effect that distinguish between plants and pollinators. The invasive species are depicted with solid orange circles."}
drake::loadd(fig_control_capacity)
library(ggplot2)
fig_control_capacity[[2]] <- fig_control_capacity[[2]] +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank())
fig_control_capacity[[4]] <- fig_control_capacity[[4]] +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank())
